Self Regulation Ontology Retest Analyses

### 2018-09-13 code/Lit_Review_Figure.Rmd
reset repo

```{r message=FALSE, echo=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '\n reference:', reference)) %>%
  filter(task_group == 'bis_bas_survey') %>%
  ggplot(aes(y = var, x = retest_reliability, label=days))+
  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#F8766D')+
  # facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  # facet_grid(task_group~.) +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'none')+
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3)),
  width=600)

>>>>

```{r message=FALSE, echo=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '\n reference:', reference)) %>%
  filter(task_group == 'bis_bas_survey') %>%
  ggplot(aes(y = var, x = retest_reliability, label=days))+
  geom_point(aes(size=sample_size, shape = type, alpha = days_cutoff), color = '#F8766D')+
  # facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  # facet_grid(task_group~.) +
  theme(#panel.spacing = unit(0.5, "lines"),
        #strip.placement = "outside",
        #strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'none'
        )+
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3)),
  width=600)

### 2018-09-13 code/SRO_Retest_Analyses.Rmd
reset repo

```{r}
p1_t_legend <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='black')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'bottom',
        axis.text.x = element_text(size=20),
        axis.title.x = element_text(size=20), 
        legend.text = element_text(size=16), 
        legend.key.width = unit(0.75, "inches"), 
        legend.title = element_text(size=20),
        legend.spacing.x = unit(0.5, "inches"),
        legend.box = "vertical",
        legend.direction = "horizontal") + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15), name="Type")+
  scale_size_continuous(name = "Sample Size", 
                        limits = c(10, 1200),
                        range = c(1, 40), 
                        breaks = c(10, 100, 1000))+
  guides(#size = guide_legend(override.aes = list(breaks = c(10, 100, 1000)), labels = c(10, 100, 1000)),
         shape = guide_legend(override.aes = list(size = 16)))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

mylegend<-g_legend(p1_t_legend)

p3_t <- arrangeGrob(arrangeGrob(p1_t, p2_t, nrow=1), mylegend, nrow=2,heights=c(10, 1))

ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 72)
```

@@

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("gray15", "gray75"))+
  xlab('Proportion of Variance in Literature Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)+
  theme(axis.title.x  = element_text(size=12),
        axis.text.x  = element_text(size=12),
        axis.text.y  = element_text(size=12),
        axis.title.y  = element_text(size=12),
        legend.title  = element_text(size=12),
        legend.text  = element_text(size=12))

ggsave('LitAndBoot_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```

@@

```{r}
rel_comp %>%
  group_by(dv, task) %>%
  summarise(mean_lit = mean(retest_reliability),
            mean_emp = unique(mean_pearson)) %>%
  ggplot(aes(mean_emp, mean_lit, col=task, shape=task))+
  geom_smooth(method="lm")+
  geom_point()+
  xlim(-0.25, 1)+
  ylim(-0.25, 1)+
  ylab("Average Literature Reliability Estimate")+
  xlab("Average Empirical Reliability Estimate")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')

ggsave('LitAndEmpAveCor.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 4, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```

@@

ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 100)
```

@@

```{r}
boot_both_w_trial = arrangeGrob(boot_task_plot, boot_survey_plot, nrow=1)

ggsave('Boot_Both_w_trialinfo.jpg', plot = boot_both_w_trial, device = "jpeg", path = "../output/figures/", width = 38, height = 48, units = "in", limitsize = FALSE, dpi = 100)
```

@@

ggsave('Bootstrap_Example_Plot_t.jpg', plot = p4, device = "jpeg", path = "../output/figures/", width = 41, height = 5, units = "in", limitsize = FALSE, dpi = 100)
```

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value, na.rm=T),
            n = n()) %>%
  mutate(cvl = qt(0.025, n-1),
         cvu = qt(0.975, n-1),
         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
         ciu = mean_pct+(sd_pct*cvu)/sqrt(n),
         sem_pct = sd_pct/sqrt(n)) %>%
  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Between subject variance",
                               "Within subject variance",
                               "Error variance")), mean_pct))+
  # geom_point(position=position_dodge(width = 0.25), size = 3, aes(color=task))+
  geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
  # geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
  geom_errorbar(aes(ymin=cil, ymax=ciu, color=task), position=position_dodge(width = 0.5), width=0.1)+
  theme_bw()+
  xlab('')+
  ylab('Percent of total variance')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=14),
        # legend.position = 'bottom',
        axis.text = element_text(size=12),
        axis.title.y = element_text(size=12))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  ylim(0,100)

ggsave('Variance_Breakdown_BarPlot.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 6, height = 5, units = "in", dpi = 300)
```

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  filter(key %in% c("avg_rt_icc", "learning_to_learn_icc", "nonperseverative_errors_icc")) %>%
  ggplot(aes((breaks+1)*10, value, shape=key))+
  geom_point()+
  geom_line(alpha = 0.5)+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  scale_shape_manual(values = c(0:9),
                     breaks = c("avg_rt_icc","learning_to_learn_icc", "nonperseverative_errors_icc"),
                     labels = c("Average Response Time", "Learning to Learn",  "Nonperseverative Errors"))

ggsave('Shift_Task_Intrameasure_Trialnum_Dependendence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
```

@@

ddm_boot_legend = arrangeGrob(ddm_boot_plot +theme(legend.position="none"),
             mylegend, nrow=2, heights=c(10, 1))

ggsave('Bootstrap_DDM_Comp_Legend.jpg', plot = ddm_boot_legend, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
```

>>>>

```{r}
p1_t_legend <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='black')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'bottom',
        axis.text.x = element_text(size=20),
        axis.title.x = element_text(size=20), 
        legend.text = element_text(size=16), 
        legend.key.width = unit(0.75, "inches"), 
        legend.title = element_text(size=20),
        legend.spacing.x = unit(0.5, "inches"),
        legend.box = "vertical",
        legend.direction = "horizontal",
        plot.caption = element_text(family = "Times", size = 40, lineheight = 2, hjust = 0)) + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15), name="Type")+
  scale_size_continuous(name = "Sample Size", 
                        limits = c(10, 1200),
                        range = c(1, 40), 
                        breaks = c(10, 100, 1000))+
  guides(#size = guide_legend(override.aes = list(breaks = c(10, 100, 1000)), labels = c(10, 100, 1000)),
         shape = guide_legend(override.aes = list(size = 16)))+
  geom_vline(xintercept = 0, color = "red", size = 1)+
  labs(caption = str_wrap("FIGURE 1: Summary of the literature review for tasks (left) and surveys (right). Each point represents a study containing test-retest reliability data on an unspecified dependent measure for a given task. The size of the point depends on the sample size of the study and the shape depends on the metric that was used to estimate reliability. Each vertical red line indicates 0 reliability.", width = 120))

@@

mylegend<-g_legend(p1_t_legend)
mycaption<-g_caption(p1_t_legend)

p3_t <- arrangeGrob(arrangeGrob(p1_t, p2_t, nrow=1), mylegend, mycaption, nrow=3, heights=c(10, 1, 1.5))

ggsave('Lit_Review_Plot_t.tiff', plot = p3_t, device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 52, units = "in", limitsize = FALSE, dpi = 250)
```

@@

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("gray15", "gray75"))+
  xlab('Proportion of Variance in Literature Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)+
  theme(#axis.title.x  = element_text(size=12),
        #axis.text.x  = element_text(size=12),
        #axis.text.y  = element_text(size=12),
        #axis.title.y  = element_text(size=12),
        #legend.title  = element_text(size=12),
        #legend.text  = element_text(size=12),
        legend.position = "bottom",
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
  labs(caption = str_wrap("FIGURE 3: Noise ceiling for comparing empirical retest reliability estimates to reliability estimates from the literature. Data come from sampling a single reliability estimate from the literature and using that as a predictor of the remaining retest reliability estimates from the literature versus using the mean estimate from our empirical results as a predictor. Models account for the effect of sample size in the literature and whether the measure is a task or survey variables. The literature samples are significantly better at predicting the rest of the literature than our empirical averages, but the distributions of variance explained across samples are highly overlapping. ", width = 120))

ggsave('LitAndBoot_Noise_Ceiling.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r}
rel_comp %>%
  group_by(dv, task) %>%
  summarise(mean_lit = mean(retest_reliability),
            mean_emp = unique(mean_pearson)) %>%
  ggplot(aes(mean_emp, mean_lit, col=task, shape=task))+
  geom_smooth(method="lm")+
  geom_point()+
  xlim(-0.25, 1)+
  ylim(-0.25, 1)+
  ylab("Average Literature Reliability Estimate")+
  xlab("Average Empirical Reliability Estimate")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
  labs(caption = str_wrap("FIGURE 2: Correlation between mean reliability estimates for each measure found in the literature with the mean reliability from our data.", width = 120))

ggsave('LitAndEmpAveCor.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r}
mycaption = textGrob(label = str_wrap("FIGURE 4: Summary of bootstrapped reliability estimates for tasks (left) and surveys (right). We sampled 150 subjects with replacement 1000 times to create a distribution of bootstrapped reliability estimate for each measure. Reliability measure depicted is ICC. Red lines indicate 0 reliability. Columns following each graph present the mean number of trials used for dependent measures in that task and the number of ‘meaningful measures,’ dependent measures used in the literature from each task.", width = 165), gp = gpar(fontfamily="Times", lineheight = 2, fontsize = 40), hjust = 0, vjust = 0.5, x = unit(0, "npc"))

boot_both_w_trial = arrangeGrob(arrangeGrob(boot_task_plot, boot_survey_plot, nrow=1), mycaption, nrow=2, heights = c(10,1))

ggsave('Boot_Both_w_trialinfo.tiff', plot = boot_both_w_trial, device = "tiff", path = "../output/figures/", width = 38, height = 55, units = "in", limitsize = FALSE, dpi = 200)
```

@@

ggsave('Bootstrap_Example_Plot_t.jpg', plot = p4, device = "jpeg", path = "../output/figures/", width = 41, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value, na.rm=T),
            n = n()) %>%
  mutate(cvl = qt(0.025, n-1),
         cvu = qt(0.975, n-1),
         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
         ciu = mean_pct+(sd_pct*cvu)/sqrt(n),
         sem_pct = sd_pct/sqrt(n)) %>%
  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Between subject variance",
                               "Within subject variance",
                               "Error variance")), mean_pct))+
  geom_errorbar(aes(ymin=cil, ymax=ciu, group=task), position=position_dodge(width = 0.25), width=0.25, size=2, alpha = 0.85, color="gray")+
  geom_point(position=position_dodge(width = 0.25), size=3, aes(color=task, shape=task))+
  #geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
  #geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
  theme_bw()+
  xlab('')+
  ylab('Percent of total variance')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=14),
        legend.position = 'bottom',
        axis.text = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  ylim(0,100)+
  labs(caption = str_wrap("FIGURE 5:  Percentage of variance explained by each of the three sources of variance: between subjects, within subjects (between sessions) and error variance for 1000 bootstrapped samples. Error bars are 95% confidence intervals.", width = 120))

ggsave('Variance_Breakdown_DotPlot.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 7, height = 4, units = "in", dpi = 300)
```

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  filter(key %in% c("avg_rt_icc", "learning_to_learn_icc", "nonperseverative_errors_icc")) %>%
  ggplot(aes((breaks+1)*10, value, shape=key))+
  geom_point()+
  geom_line(alpha = 0.5)+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
                             plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
  scale_shape_manual(values = c(0:9),
                     breaks = c("avg_rt_icc","learning_to_learn_icc", "nonperseverative_errors_icc"),
                     labels = c("Average Response Time", "Learning to Learn",  "Nonperseverative Errors")) +
  labs(caption = str_wrap("FIGURE 6: Change in point estimates of ICC for three dependent measures selected from the Shift task using increasing numbers of trials to estimate them. These measures show the different types of relationships reliability estimates have based on the trial numbers used to estimate them.", width = 180))

ggsave('Shift_Task_Intrameasure_Trialnum_Dependendence.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 300)
```

@@

mycaption = textGrob(label = str_wrap("FIGURE 7: Average bootstrapped reliability estimates per measure comparing raw measures and model parameters as well as contrast and non-contrast measures for task measures.", width = 130), gp = gpar(fontfamily="Times", lineheight = 2, fontsize = 18), hjust = 0, vjust = 0.5, x = unit(0, "npc"))

ddm_boot_legend = arrangeGrob(ddm_boot_plot +theme(legend.position="none"),
             mylegend, mycaption, nrow=3, heights=c(10, 1, 1))

ggsave('Bootstrap_DDM_Comp_Legend.tiff', plot = ddm_boot_legend, device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE, dpi=300)
```
